---
title: "Arnold in the wild"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Who's Arnold?

Smart Energi is a cooperation between a number of District Heating companies in Sweden. Together they have developed the application `K2` which is used for outlier detection in District Heating systems. For each metering point in a DH-system `K2` will detect outliers and provide an Energy Analyst with a alarms if outliers are detected. `K2` uses an algorithm developed by `Chalmers University` called `Kasper` but it is somewhat enhanced by `Smart Energi`.

The algorithm `Arnold` is a development of the `Kasper`-algorithm. One difference between the two algorithms is that `Arnold` uses a non linear regression technique called `Generalized Additive Models`(GAM) while `Kasper` uses a piecewise regression. However, the main distinction between the two algorithms is that `Kasper` needs reference data (that should be manually selected by the Energy Analyst) while `Arnold` does not, although `Arnold` can be configured to use reference data if needed.

If you want to know more about `Arnold`, you can read an introduction to it here: 
And Ida Lundholm Benzi have written an excellent explanation of `Kasper` here:

In this Notebook we'll explore how `Arnold` works on a larger dataset.

## Data from Öresundskraft

In the BRAVA Datalake we have data that originally comes from Öresundskraft, but it is provided to BRAVA by Halmstad University who have used the data in the development of their outlier detection algorithm that you can read more about in their notebook [Conformal anomaly sequence detection via the reference-group based approach: a study on district heating substations](https://kyso.io/smartenergi/conformal-anomaly-sequence-detection-via-the-reference-group-based-approach-a-study-on-district-heating-substations?team=smartenergi).

The data consist of hourly district heating consumption with around 12 000 metering points. Morever, as any dataset in the BRAVA Datalake the 

```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(dbplyr)
library(DBI)
library(odbc)
library(gt)
```

For this Notebook we'll limit ourselves to using Arnold on daily `energy` data and not `flow`. This is the same data that is used in K2. Furthermore, daily data drastically reduces the computation needed to perform outlier detection

```{r}
con <- dbConnect(odbc::odbc(), Driver = "Snowflake", Server = "lq42418.eu-west-1.snowflakecomputing.com", 
    uid = "filipw", Database = "SMARTENERGI_DATALAKE_SANDBOX", pwd = keyring::key_get("smartenergi"))

tbl(con, in_schema("PUBLIC", "ORKAFT_METER_READINGS_TBL")) %>% 
  filter(PROPERTY == "energy") %>% 
  head()
```

## Exploring data

## Using `Arnold`

## Write to Database

## How many alarms are produced?